\message{ !name(trip-liability.tex)}\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{times}
\usepackage{amsmath,amsthm, amssymb, latexsym}
\usepackage[abbr]{harvard}


\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}


\textwidth = 7 in
\textheight = 9.5 in
\oddsidemargin = -0.25 in
\evensidemargin = -0.25 in
\topmargin = -0.5 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}

\title{Liability Release and Assumption of Risk Agreement}
\author{Pro Scuba Training, LLC}
\date{}
\begin{document}

\message{ !name(trip-liability.tex) !offset(-3) }


\pagenumbering{gobble}

\begin{center}
{\Large {\bf Liability Release and Assumption of Risk Agreement}}\\
\end{center}

{\bf Please read carefully and fill in all the blanks before signing.}

I \makebox[3in]{\hrulefill} , hereby affirm that I am voluntarily engaging in the recreational activities planned for the trip to \underline{\hspace{1in}} arriving on \underline{\hspace{.5in}} and ending on \underline{\hspace{.5in}}, which activities may include, but not limited to: scuba diving, snorkeling, free-diving, boating, swimming and any other activities that are made possible because of this trip. If I engage in scuba diving, I affirm that I am a certified diver or a student under the control and supervision of a certified scuba instructor, and that I am aware that planned water activities such as skin and scuba diving have inherent risks that may result in serious injury or death. I certify that I am fully aware and expressly assume all risks that may be associated with my involvement in: scuba diving, snorkeling, free-diving, boating, swimming and any other activities that are made possible because of this charter.

I understand and agree that neither {\bf Pro Scuba Training, LLC}, {\bf Christopher L. Simpkins}, {\bf Georgia Institute of Technology}, {\bf GT Scuba}, {\bf PADI Inc.} nor any of their affiliate or subsidiary corporations, nor the owners, officers, employees, agents, contractors, or assigns of the above listed entities (hereinafter referred to as “Released Parties”) may be held liable or responsible in any way for injury, death or damages to me, my family, estate, heirs or assigns that may occur as a result of my participation of this trip or as a result of the negligence of any party, including the Released Parties, whether passive or active.

I further state that I am of lawful age and legally competent to sign this Liability Release Agreement, or I have obtained written consent from my parent or guardian. I understand that terms herein are contractual and not a mere recital, and that I have signed this agreement of my own free act and with the knowledge that I hereby agree to waive my legal rights. I further agree that if any provision of this agreement is found to be unenforceable or invalid, that provision shall be severed from this agreement. The remainder of this agreement will then be construed as though the enforceable provision had never been contained herein.

I understand and agree that I am not only giving up my right to sue the Released Parties but also any rights that my heirs, assigns, or beneficiaries may have to sue the Released Parties resulting from my death. I further represent I have the authority to do so and that my heirs, assigns or beneficiaries will be stopped from claiming otherwise because of my representations to the Released Parties.

I \makebox[3in]{\hrulefill} , BY THIS INSTRUMENT, AGREE TO EXEMPT AND RELEASE ALL THE ABOVE LISTED ENTITIES AND/OR INDIVIDUALS, WHETHER SPECIFICALLY NAMED OR NOT, FROM ALL LIABILITY AND RESPONSIBILITY FOR PERSONAL INJURY, PROPERTY DAMAGE OR WRONGFUL DEATH, HOWEVER CAUSED, INCLUDING BUT NOT LIMITED TO, PRODUCT LIABILITY OR THE NEGLIGENCE OF THE RELEASED PARTIES, WHETHER PASSIVE OR ACTIVE.

I HAVE FULLY INFORMED MYSELF AND MY HEIRS OF THE CONTENTS OF THIS LIABILITY RELEASE AND ASSUMPTION OF RISK AGREEMENT BY READING IT BEFORE SIGNING IT ON BEHALF OF MYSELF AND MY HEIRS.\\

\begin{tabular}{lcr}\\
\makebox[3.5in]{\hrulefill} & \hfill & \makebox[2in]{\hrulefill} \\
Signature of Participant    & \hfill & Date (Day/Month/Year) \\
\makebox[3.5in]{\hrulefill} & \hfill & \makebox[2in]{\hrulefill} \\
Signature of Parent or Guardian (where applicable) & \hfill & Date (Day/Month/Year) \\
\end{tabular}

\end{document}

\message{ !name(trip-liability.tex) !offset(-66) }
